Proposed Solution

### 2016-11-14 Ennan-Proposal/travis.tex
intro, with news

Version space learning builds a logical constraint model for binary
classification~\cite{mitchell77}, which we use to test a configuration file for membership
in the set of all correct files.
Traditionally, version space learning builds a model that defines membership using a series of disjunctions from a set of predefined hypotheses. However, we need  to use conjunctions to convey that a configuration file is only correct if it satisfies all the learned relations, as

>>>>

Version space learning builds a logical constraint model for binary
classification~\cite{mitchell77}, which we use to test a configuration file for membership
in the set of all correct files.

We extend the \app's functionality to first learn the rules that have 
to hold for correct TravisCI configuration files. Traditionally, 
version space 
learning builds a model that defines membership using a series of 
disjunctions from a set of predefined hypotheses.  However, we need  to 
use conjunctions to convey that a configuration file is only correct if 
it satisfies all the learned relations. Those rules can be seen as
positive examples in classifying correct files. In addition, we will have
so-called {\emph {breaking rules}} which are derived from the files 
that do not compile, \ie negative examples. Breaking rules are specified 
using disjunctions.
